Hydra battles in Coq

### 2020-10-19 doc/hydras.tex
new tactics for navigating in the hydra

@@

\subsubsection{Example}
Let us prove the transformation of \texttt{Hy'} into \texttt{Hy''} (see Fig.~\vref{fig:Hy3}).

@@

\begin{Coqsrc}
Example R2_example:  R2 4 Hy' Hy''.
Proof.
  right. right. left.  right. left. left. left. split. left.
Qed.
\end{Coqsrc}

@@

>>>>

% \begin{verse}
% Hydra hydra hydram \\

% Hydrae hydrae hydra \\

% Hydrae hydrae hydras \\

% Hydrarum hydris hydris\\
% \end{verse}

@@

\subsubsection{Example}
Let us prove the transformation of \texttt{Hy'} into \texttt{Hy''} (see Fig.~\vref{fig:Hy3}). We use an experimental set of tactics for specifying place where the interaction between Hercules and the hydra holds.

@@

\begin{Coqsrc}
Example R2_example:  R2 4 Hy' Hy''.
Proof.
    (** move to 2nd sub-hydra (0-based indices) *) R2_up 1. 
    (** move to first sub-hydra *)  R2_up 0.
    (** we're at distance 2 from the to-be-chopped-off head 
        let's go to the first daughter, then chop-off the leftmost head *)
    last_two 0 0. 
Qed.
\end{Coqsrc}

@@

\begin{project}
The library \texttt{Hessenberg} looks too long (proof scripts and compilation).
Please try to make it simpler and more efficient!
Thanks!
\end{project}
